Thesis outline

### 2017-06-16 KellyDouglass/Thesis/Thesis_sections/Paper3.tex
Added Paper 3

\chapter{Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass}\label{ch:Paper3}

@@

>>>>

\chapter[O$^+$ approximation]{Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass}\label{ch:Paper3}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    ABSTRACT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{chapabstract}
We study how the void environment affects the chemical evolution of galaxies in 
the universe by comparing the oxygen and nitrogen abundances of dwarf galaxies 
in voids with dwarf galaxies in denser regions.  Using spectroscopic 
observations from the Sloan Digital Sky Survey Data Release 7, we estimate the 
oxygen and nitrogen abundances of 993 void dwarf galaxies and 759 dwarf galaxies 
in denser regions.  We use the Direct $T_e$ method for calculating the gas-phase 
chemical abundances in the dwarf galaxies because it is best suited for low 
metallicity, low mass (dwarf) galaxies.  A substitute for the [\ion{O}{2}] 
$\lambda 3727$ doublet is developed, permitting oxygen abundance estimates of 
SDSS dwarf galaxies at all redshifts with the Direct $T_e$ method.  We find that 
void dwarf galaxies have slightly higher oxygen abundances ($\sim$7\%) than 
dwarf galaxies in denser environments.  The opposite trend is seen in both the 
nitrogen abundance and N/O ratio: void dwarf galaxies have slightly lower 
nitrogen abundances ($\sim$10\%) and lower N/O ratios ($\sim$17\%) than dwarf 
galaxies in denser regions.  Our mass-N/O relationship shows that the secondary 
production of nitrogen commences at a lower stellar mass in void dwarf 
star-forming galaxies than in dwarf star-forming galaxies in denser 
environments.  We also find that star-forming void dwarf galaxies have higher 
\ion{H}{1} masses than the star-forming dwarf galaxies in denser regions.  Our 
star-forming dwarf galaxy sample demonstrates a strong anti-correlation between 
the sSFR and N/O ratio, providing evidence that oxygen is produced in higher 
mass stars than those which synthesize nitrogen.  The lower N/O ratios and 
smaller stellar mass for secondary nitrogen production seen in void dwarf 
galaxies may indicate both delayed star formation as predicted by $\Lambda$CDM 
cosmology and a dependence of cosmic downsizing on the large-scale environment.  
The shift toward higher oxygen abundances and higher \ion{H}{1} masses in void 
dwarf galaxies might be evidence of larger ratios of dark matter halo mass to 
stellar mass in voids than in denser regions.
\end{chapabstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    INTRODUCTION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

% Primary v. secondary production of nitrogen (reminder) & its influence on the CNO cycle
%% What would cause less nitrogen to be produced in void galaxies?
%Lower production rates of nitrogen relative to oxygen production in void dwarf 
%galaxies could be a consequence of the retarded star formation predicted for 
%dwarf galaxies in voids by the $\Lambda$CDM cosmology.  In stellar 
%nucleosynthesis, there are two main classes of elements: primary and secondary.  
%Primary elements are those produced which do not depend on the quantity of any 
%other elements present in the star (excepting hydrogen, of course).  On the 
%other hand, secondary elements can be synthesized only when other elements are 
%already present in the star at the time of its birth.  Oxygen is a primary 
%element in stellar nucleosynthesis.  There is evidence 
%\textcolor{red}{(SOURCES)} to suggest that nitrogen behaves as both a primary 
%and secondary element.  The main source of nitrogen production is during the CNO 
%cycle, where carbon is needed as a catalyst for the reactions to begin.  If a 
%star is born with enough carbon, then it commences the CNO cycle much earlier 
%than in a star created with only hydrogen (or with only trace amounts of 
%carbon).  If star formation is retarded in void dwarf galaxies, then there are 
%fewer of the heavy elements that have been produced up to this point in time.  
%As a result, the stars that are created have less carbon initially present in 
%the star than in stars within wall dwarf galaxies, and less nitrogen will be 
%produced.  Fig. \ref{fig:N_1sig} shows evidence of this fact --- there is 
%slightly less nitrogen in void dwarf galaxies than in the dwarf galaxies in more 
%dense environments.

% Prominence of voids in large-scale structure 
% (refs up through Pan et al., other recent void catalogs, ref to van Weygaert review)
Galactic redshift surveys have revealed that the large-scale distribution of 
galaxies is similar to a three-dimensional cosmic web \citep{Bond96}, with thin 
filaments of galaxies connecting galaxy clusters separated by voids (large, 
underdense areas which fill more than 60\% of space).  The voids first 
identified in early surveys \citep[e.g.,][]{Gregory78,Kirshner81,deLapparent86} 
have proven to be a universal feature of large-scale structure.  Analyses of the 
Sloan Digital Sky Survey \citep{Abazajian09,Ahn12} have produced catalogs of 
$10^3$ voids \citep{Pan12,Sutter14}.  Cosmic voids are an essential component for 
understanding the role of a galaxy's environment on its formation and evolution 
\citep[see][for a review]{vandeWeygaert11}.

% Influence of the large-scale environment on galaxy properties
%  - well-established morphology-density relation (refs starting with Dressler 1980; Postman & Geller 1984)
%  - morphology-luminosity-density (Park et al. 2005?)
%  - evidence that trend continues into voids, where galaxies are found to be bluer, later type, higher sSFR (Rojas et al. 2004, 2005, who attribute this to availability of cool gas to feed star formation, and other refs)
%  - shift of void galaxy luminosity function (Hoyle et al.; Moorman et al.)
%  - consistent with shift of dark matter halo mass function (Goldberg et al.)
%  - investigations of HI properties of void galaxies (Kreckel et al., Moorman et al.)
%  - other refs to "Void galaxy survey" by Kreckel, van de Weygaert et al.
Extensive studies have been performed to understand the role of the environment 
in galaxy formation.  A strong relationship was found between a galaxy's 
morphology and the local density \citep{Dressler80,Postman84}, where the 
fraction of early-type galaxies increases with density.  A galaxy's luminosity 
was found to also contribute to this morphology-luminosity-density relation 
\citep{Park07}.  While much of this early work focused on trends of galaxy 
properties in the densest regions of space, evidence was found that the same 
trends persist into the voids, where galaxies are found to be bluer 
\citep{Grogin99,Rojas04,Patiri06,vonBendaBeckmann08,Hoyle12}, of a later 
morphological type \citep{Grogin00,Rojas04,Park07}, and have higher specific 
star formation rates \citep[sSFR;][]{Rojas05,vonBendaBeckmann08,Moorman15,
Beygu16}.  These trends are attributed to the availability of cool gas to feed 
star formation in the void regions.  \cite{Hoyle05} and \cite{Moorman15} showed 
that there is a shift toward fainter objects in the void galaxy luminosity 
function.  This shift is consistent with the predicted shift of the dark matter 
halo mass function \citep{Goldberg05}.  Investigations into the \ion{H}{1} 
properties of void galaxies have also been performed \citep{Kreckel12,
Moorman14}, where void galaxies tend to have lower \ion{H}{1} masses than 
galaxies in denser environments.  All these observations are consistent with 
predictions from the $\Lambda$CDM cosmology that void galaxies have lower masses 
and be retarded in their star formation when compared to those in denser 
environments \citep[e.g.,][]{Gottlober03,Goldberg05,Cen11}.

% If sSFR are different, and evolutionary history different, is chemical evolution different?
% Suggestions from previous work (Pustilnik et al, others) of very low metallicity in void galaxies
Given that the sSFR and evolutionary history are different for galaxies in 
voids, it follows that their chemical evolution might also be influenced by the 
environment.  The metallicity of a galaxy (a measure of the integrated star 
formation history) is an estimate of the percentage of the galaxy's gas that has 
been processed in stars \citep{Guseva09}.  We would expect void galaxies to have 
lower metallicities than those in denser regions if they have only recently 
commenced forming stars or have recently accreted unprocessed gas.  Observations 
by \cite{Cooper08,Deng11,Filho15,Pustilnik06,Pustilnik11a,Pustilnik11b,
Pustilnik13,Pustilnik14}, and \cite{Pilyugin17} support the hypothesis that void 
galaxies have lower metallicities than galaxies in denser regions.  However, 
\cite{Kreckel15} and \cite{Douglass17a} find no influence from the large-scale 
environment on the metallicity, and \cite{Douglass17b} find that void dwarf 
galaxies have higher metallicities than dwarf galaxies in denser regions.  It is 
obvious that a study of a statistically significant large sample of galaxies is 
required to understand how the large-scale environment influences the chemical 
evolution of galaxies.

% Forcus on dwarf galaxies, which are most sensitive to effects of environment
% SDSS allows void catalog (Pan et al.) and identification of statistically-significant samples of dwarf galaxies (Mr > -17) in voids
% Discuss importance of careful use of metallicity (O/H) estimators - commonly used methods not calibrated for low mass galaxies, so we carefully used "direct" method
% Summary of results in Douglass & Vogeley 2017a,b
Environmental effects should be the most obvious on dwarf galaxies, since they 
possess small gravitational potential wells.  As a result, they are more 
sensitive to astrophysical effects such as cosmological reionization, internal 
feedback from supernova and photoheating from star formation, external effects 
from tidal interactions and ram pressure stripping, small-scale details of dark 
matter halo assembly, and properties of dark matter.  The main galaxy sample of 
SDSS DR7 covers a large enough volume to identify over 1000 voids \citep{Pan12} 
along with a statistically-significant sample of dwarf galaxies ($M_r > -17$) in 
voids.  SDSS also provides spectroscopy that permits metallicity estimates of 
this large sample of dwarf galaxies.

Numerous methods to estimate the metallicity of an object have been developed 
over the years, as a result of the availability of various spectral features.  
All methods except the direct $T_e$ method are calibrated on galaxies with 
various characteristics, making it unwise to apply them to galaxies outside the 
groups from which these calibrations were derived.  The commonly used methods 
are not calibrated for low-mass galaxies, so we carefully chose to use the 
Direct $T_e$ method because we are focusing on only dwarf galaxies.  A detailed 
explanation of this and other method classes can be found in \cite{Douglass17a}.  
With this estimator, \cite{Douglass17a} and \cite{Douglass17b} have looked at 
the gas-phase chemical abundances of 135 star-forming dwarf galaxies.  They 
found that the large-scale environment has very little influence on the oxygen 
and nitrogen abundances in star-forming dwarf galaxies.  However, their sample 
does indicate that star-forming void galaxies have lower N/O ratios than 
star-forming dwarf galaxies in denser regions.  This is attributed to delayed 
star formation in void galaxies, along with a possible environmental influence 
on cosmic downsizing.  They also argue that the very slight shift towards higher 
oxygen abundances in star-forming void dwarf galaxies could be due to a larger 
ratio of dark matter halo mass to stellar mass in void dwarf galaxies.

% In this paper...
% New approach to O abundance estimation - allows use of larger sample.  Still using "direct" method.
% Note that this work examines dwarf, star-forming galaxies only
% Here we also examine HI properties
% Known influence of environment on morphology already taken into account (well, not exactly because we select on emission lines, not morphology from photometry) - we look only at star-forming galaxies
% Known influence of environment on luminosity already taken into account - we look only at dwarfs
We look to expand on the work by \cite{Douglass17a,Douglass17b} by substantially 
increasing their sample size of dwarf galaxies.  The main limiting factor in 
their sample was due to the required detection of the [\ion{O}{2}] $\lambda$3727 
doublet, which is needed to estimate the amount of singly-ionized oxygen 
present.  We present a new approach to the O$^+$ abundance estimation, which 
removes the need for this emission line.  This calculation is used in 
conjunction with the Direct $T_e$ method to estimate the total gas-phase oxygen 
abundance in galaxies.  We also examine the relationship between the chemical 
abundance and \ion{H}{1} mass of star-forming dwarf galaxies.  For reasons 
described above, this work only examines the chemical evolution of star-forming 
dwarf galaxies.  As a result of this sample, the known influences of the 
environment on the morphology and luminosity have already be taken into account, 
since we concentrate only on star-forming dwarf galaxies.

% THEORY
% Discuss above as motivation or save for Discussion? - save for discusson (KAD)
% Ref Cen simulation paper that shows that void have cool gas available for star formation
% Ref Tonnesen & Cen simulation paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    THEORY
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Theory]{Estimation of gas-phase chemical abundances from optical spectroscopy}

We study a galaxy's oxygen and nitrogen abundances for several key reasons.  
These two elements are relatively abundant and emit strong lines in the optical, 
including for several ionization states in oxygen, making them relatively easy 
to observe \citep{Kewley02}.  In addition, a ratio of oxygen's lines provides a 
good estimate of the electron temperature, allowing for reliable measurements of 
a galaxy's gas-phase chemical abundances.  The following is an explanation of 
the theory and methods we employ to estimate the oxygen and nitrogen abundances 
in dwarf galaxies.

% ------------------------------------------------------------------------------
\subsection{Direct $T_e$ method}\label{sec:DirectTe}

We use the Direct $T_e$ method described in \cite{Izotov06} to estimate the 
gas-phase abundances of oxygen and nitrogen in our sample of dwarf galaxies, 
because this method is often regarded as the most accurate estimate of element 
abundances.  It can be difficult to use due to the nature of the [\ion{O}{3}] 
$\lambda$4363 auroral line \citep[for a more detailed discussion, see][]
{Douglass17a}.  Since the strength of [\ion{O}{3}] $\lambda$4363 is inversely 
proportional to the metallicity of a galaxy, it is best suited for low-redshift, 
low-metallicity galaxies.  At metallicities 
$12 + \log (\text{O}/\text{H}) \gtrsim 8.5$, [\ion{O}{3}] $\lambda$4363 becomes 
too weak to detect in the SDSS spectra.  With the mass-metallicity (MZ) relation 
by \cite{Tremonti04}, this metallicity limit corresponds to a maximum stellar 
mass of
\begin{align*}
    12 + \log \left( \frac{\text{O}}{\text{H}} \right) &= -1.492 + 1.847(\log M_*) - 0.08026(\log M_*)^2\\
    8.5 &= \\
    \log \left( \frac{M_*}{M_\odot} \right) &= 8.696
\end{align*}
The MZ relation by \cite{Andrews13} estimates that this maximum metallicity 
translates to a maximum stellar mass of
\begin{align*}
    12 + \log \left( \frac{\text{O}}{\text{H}} \right) &= 12 + \log \left( \frac{\text{O}}{\text{H}} \right)_{asm} - \log \left( 1 + \left( \frac{M_{TO}}{M_*} \right)^\gamma \right)\\
    8.5 &= 8.798 - \log \left( 1 + \left( \frac{10^{8.901}}{M_*} \right)^{0.640} \right)\\
    M_* &= 8.138\times 10^8 M_\odot\\
    \log \left( \frac{M_*}{M_\odot} \right) &= 8.911
\end{align*}
These upper limits on the galaxy stellar masses correspond to the maximum mass 
of a dwarf galaxy in SDSS ($\log (M_*/M_\odot) \approx 9$).  Therefore, we can 
expect to estimate the chemical abundances of only dwarf galaxies in SDSS DR7 
with the Direct $T_e$ method.  Higher resolution spectra would be necessary to 
probe higher mass, higher metallicity galaxies.

After solving for the temperature of the gas, we can 
calculate the amount of each element present in each of the ionization stages.  
The total gas-phase oxygen abundance is equal to the sum of the abundances of 
each of the ionized populations:
\begin{equation}
	\frac{\text{O}}{\text{H}} = \frac{\text{O}^{++}}{\text{H}^+} + \frac{\text{O}^+}{\text{H}^+}
\end{equation}

We use an ionization correction factor (ICF) to account for the missing stages 
of nitrogen, since we can observe nitrogen in only one of its main ionization 
stages.  The total abundance for a particular element $X$ is 
\begin{equation}
    \frac{\text{X}}{\text{H}} = \sum_i ICF_i \frac{\text{X}^i}{\text{H}}
\end{equation}
For nitrogen, we employ the ICFs used in \cite{Douglass17b}.

% ------------------------------------------------------------------------------
\subsection{O$^+$ abundance approximation}\label{sec:Oplus_approx}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper3/Zlow_v_Zreal_1sig_I06_BPTclass_fits}
    \caption{$12 + \log{\text{O}^{++}/\text{H}}$ versus 
    $12 + \log{\text{O}/\text{H}}$ for those galaxies with $M_r > -20$ as 
    calculated with the direct method; the galaxies are colored by their 
    classification in the BPT diagrams (from \cite{Brinchmann04}).  Two linear 
    models have been fit to three groups in the sample: star-forming and 
    AGN/composite galaxies; the best fit parameters can be found in Table 
    \ref{tab:ab}.}
    \label{fig:lowVreal}
\end{figure}

We derive an ICF for O$^+$ to overcome some limitations on the observations of 
dwarf galaxies in SDSS to bolster our sample size.  Because we are studying 
dwarf galaxies, the [\ion{O}{2}] $\lambda 3727$ doublet necessary for estimating 
the abundance of O$^+$ is only available for objects within the redshift range 
$0.02 < z < 0.03$ \citep[see Sec. \ref{sec:SDSS_limits} and][for more 
details]{Douglass17a}.  To be able to study SDSS galaxies at redshifts less than 
0.02, we need to find an alternate way to estimate the abundance of O$^+$.  
Ordinarily, we would use an ICF to replace the missing ionization stage, as 
outlined in Sec. \ref{sec:DirectTe} for the nitrogen abundance.  Because the 
[\ion{O}{2}] $\lambda 3727$ emission line is normally available for analysis, 
there are no approximations available for the ICF for the amount of 
singly-ionized oxygen.  To construct an ICF appropriate for our dwarf galaxy 
sample, we compare $12 + \log{\text{O/H}}$ to 
$12 + \log{\text{O}^{++}/\text{H}}$ as calculated by the Direct $T_e$ method for 
all galaxies in SDSS with $M_r > -20$.  Recognizing that the relative amounts of 
singly- and doubly-ionized oxygen will depend on the hardness of a galaxy's 
spectrum, we use a Baldwin-Phillips-Terlevich (BPT) diagram \citep{Baldwin81} to 
classify each galaxy as star-forming, AGN, or composite (containing 
characteristics of both a star-forming region and an AGN).  Noting a strong 
separation in the relationship between O$^{++}$/H and O/H with respect to the 
galaxies' BPT classifications by \cite{Brinchmann04}, we fit two linear models 
to the sample, seen in Fig. \ref{fig:lowVreal} and defined as 
\begin{equation}\label{eq:fit}
    12 + \log{\text{O}/\text{H}} = a(12 + \log{\text{O}^{++}/\text{H}}) + b
\end{equation}
The values for $a$ and $b$ for the two classes are listed in Table \ref{tab:ab}.

\floattable
\begin{deluxetable}{L|C|C|C}
    \tablewidth{0pt}
    \tablecaption{Coefficients of oxygen abundance fits\label{tab:ab}}
    \tablehead{\colhead{} & \colhead{SF (dwarf)} & \colhead{SF ($M_r > -20$)} & \colhead{AGN \& Composite}}
    \startdata
        a & 0.84 \pm 0.013 & 0.824 \pm 0.0010 & 0.764 \pm 0.0035\\
        b & 1.61 \pm 0.094 & 1.787 \pm 0.0065 & 2.05 \pm 0.023\\
    \enddata
    \tablecomments{Coefficients for the linear trends (Eqn. \ref{eq:fit}) fit to 
    the SF galaxies (dwarf and those with $M_r > -20$) and AGN and composite 
    galaxies.  With these trends, we can now calculate the total oxygen 
    abundance for a galaxy with knowing only the O$^{++}$/H abundance.}
\end{deluxetable}

As expected, the star-forming galaxies have less doubly ionized oxygen than 
both the composite and AGN galaxies.  Since the degree of ionization depends on 
the temperature of the stars ionizing the gas, this means that the star-forming 
galaxies have cooler ionizing sources than the composite and AGN galaxies.

For those star-forming dwarf galaxies for which [\ion{O}{2}] $\lambda$3727 is 
not observed in the SDSS spectra, we use the coefficients for the star-forming 
dwarf galaxies with Eqn. \ref{eq:fit} to calculate the total oxygen abundance in 
the galaxy based on the amount of doubly-ionized oxygen found with Eqn. 4 of 
\cite{Douglass17a}.  While we list the coefficients for the linear models of 
both those galaxies with absolute magnitudes $-17 > M_r > -20$ and the AGN and 
composite galaxies in Table \ref{tab:ab}, we do not use them to calculate the 
chemical abundances of these galaxies for the reasons outlined in Section 
\ref{sec:DirectTe}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    DATA
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SDSS data and galaxy selection}

The SDSS Data Release 7 (DR7) \citep{Abazajian09} is a wide-field multiband 
imaging and spectroscopic survey employing a drift scanning technique to map 
approximately one-quarter of the northern sky.  Photometric data in the 
five-band SDSS system --- $u$, $g$, $r$, $i$, and $z$ --- are taken with a 
dedicated 2.5-meter telescope at the Apache Point Observatory in New Mexico 
\citep{Fukugita96, Gunn98}.  Follow-up spectroscopic analysis is performed on 
galaxies with a Petrosian $r$-band magnitude $m_r < 17.77$ \citep{Lupton01, 
Strauss02}.  The spectra are taken using two double fiber-fed spectrometers and 
fiber plug plates with a minimum fiber separation of 55"; the observed 
wavelength range is $3800\text{\AA}$ to $9200\text{\AA}$ with a resolution 
$\lambda / \Delta \lambda \sim$1800 \citep{Blanton03}.  We use emission-line 
flux data from the MPA-JHU value-added catalog\footnote{Available at 
\url{http://www.mpa-garching.mpg.de/SDSS/DR7/}}, which is based on the SDSS DR7 
sample of galaxies.  All flux values have been corrected for dust reddening with 
the \cite{Cardelli89} extinction curve as implemented in pyNeb 
\citep{Luridiana15}; we assume the theoretical ratio H$\alpha$/H$\beta = 2.86$ 
at 10,000 K and 100 cm$^{-3}$ \citep{Osterbrock89}.

We use the stellar mass estimates from the NASA-Sloan Atlas \citep{Blanton11}.  
The \ion{H}{1} mass estimates are from the 70\% complete ALFALFA catalog 
$\alpha.70$ \citep{Giovanelli05}; \ion{H}{1} detections were matched to the SDSS 
galaxies by locating the nearest optical counterpart identified in the 
$\alpha.70$ catalog within 1 arcmin.  Absolute magnitudes, colors, and all other 
additional data are from the KIAS value-added galaxy catalog 
\citep{Choi10,Blanton05}.  Galaxy colors are rest-frame colors which have been 
$K$-corrected to a redshift of 0.1; they are corrected for galactic extinction 
and calculated with model magnitudes.  All galaxies have been visually inspected 
to remove any galaxy fragments or duplicates.

%-------------------------------------------------------------------------------
\subsection{Spectroscopic selection}\label{sec:SDSS_limits}

We employ the same requirements for our sample as in 
\cite{Douglass17a,Douglass17b}: all galaxies must have
\begin{enumerate}
    \item{$M_r > -17$ (dwarf galaxies);}
    \item{a minimum $5\sigma$ detection of H$\beta$;}
    \item{a minimum $1\sigma$ detection of [\ion{O}{3}] $\lambda 4363$;}
    \item{a flux $> 0$ for [\ion{O}{2}] $\lambda 3727$, [\ion{O}{3}] $\lambda \lambda 4959,5007$, and [\ion{N}{2}] $\lambda \lambda 6548,6584$;}
    \item{$T(\text{[\ion{O}{3}]}) > 3\times 10^4 \text{ K}$;}
    \item{a star-forming BPT classification by \cite{Brinchmann04}.}
\end{enumerate}

For those galaxies with a redshift $z \gtrsim 0.02$, we use the 
\texttt{oii\_flux} value from the MPA-JHU catalog in place of their [\ion{O}{2}] 
$\lambda \lambda 3726,3729$ flux measurement.  See \cite{Douglass17a} for 
further details on each of these requirements.

%-------------------------------------------------------------------------------
\subsection{Void classification}
% Re-write to avoid plagarizing myself :P

Void galaxies are identified using the void catalog compiled by \cite{Pan12}, 
which was built based on the galaxies in SDSS DR7 catalog.  Starting with 
galaxies with absolute magnitudes $M_r < -20$, the VoidFinder algorithm of 
\cite{Hoyle02} \citep[based on the algorithm described by][]{ElAd97} removes all 
isolated galaxies (defined as having the third nearest neighbor more than 7 
$h^{-1}$ Mpc away).  After applying a grid to the remaining galaxies, spheres 
are grown from all empty grid cells (cells containing no galaxies).  A sphere 
reaches its maximum size when it encounters four galaxies on its surface.  To be 
classified as a void (or part of one), a sphere must have a minimum 10 Mpc 
radius.  If two spheres overlap by more than 10\%, they are considered part of 
the same void.  See \cite{Hoyle02} for a more detailed description of the 
VoidFinder algorithm.  Those galaxies that fall within these void spheres are 
classified as voids.  Those galaxies that lie outside the spheres are classified 
as wall galaxies.  Because we cannot identify any voids within 10 Mpc of the 
edge of the survey, we do not include the galaxies that fall within this region 
in either the void or wall sample (throughout this paper, these galaxies are 
labeled as ``Uncertain'').

Of the $\sim$800,000 galaxies with spectra available in SDSS DR7, 9519 are 
dwarf galaxies.  Applying the spectroscopic cuts, our sample includes 993 void 
dwarf galaxies and 759 wall dwarf galaxies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    ANALYSIS & RESULTS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Abundance analysis and results}

Our primary objective is to perform a relative measurement of gas-phase 
abundances of dwarf galaxies to discern how their chemical evolution is affected 
by the large-scale environment.

%Our primary objective is to perform a relative measurement of metallicity of 
%dwarf galaxies to discern how the large-scale environment affects their chemical 
%evolution.  As discussed in Section \ref{sec:Theory}, the strength of and 
%ability to observe different spectral lines between various surveys and 
%observations require multiple methods to be developed for metallicity 
%calculations.  In this paper, we use only the Direct $T_e$ method, because no 
%other method has yet been calibrated using dwarf galaxies.  The results from the 
%various methods are not directly comparable; while they all return metallicities 
%within the same range, the same galaxy can have very different metallicity 
%values depending on which method is used.  Conversions between methods have been 
%developed \citep[see][]{Kewley08}, but it is not clear that these conversions 
%would be accurate for dwarf galaxies.  Unfortunately, there are not enough 
%galaxies available in our sample to calibrate these other methods for dwarf 
%galaxies.

All line ratios listed are ratios of the emission-line fluxes.  Galaxies with 
low metallicities have $Z = 12 + \log (\text{O}/\text{H}) < 7.6$ 
\citep{Pustilnik06}; galaxies with high metallicities have $Z > 8.2$ 
\citep{Pilyugin06}.  The solar metallicity $Z_\odot = 8.86$ \citep{Delahaye06}.

%-------------------------------------------------------------------------------
\subsection{Estimation of uncertainties}

% Uncertainties
Uncertainties in the computed abundances are estimated using a Monte-Carlo 
method.  Using the measured line fluxes and scaled uncertainty estimates, we 
calculate 100,000 abundance estimates.  For each abundance estimate, a new 
positive ``fake'' line flux is drawn from a normal distribution.  We use the 
standard deviation in these sets of 100,000 calculated abundance values for the 
error in our abundance estimate.  See \cite{Douglass17a} for a more in-depth 
description of this process.

%-------------------------------------------------------------------------------
\subsection{Sources of systematic error}

Many physical properties of galaxies exhibit a radial dependence \citep{Bell00}.  
As a result, abundance estimates can depend on where the spectroscopic fiber is 
placed on the galaxy.  The estimated abundance will not necessarily be 
representative of a global abundance value if not all of the galaxy's light is 
contained within the fiber.  \cite{Belfiore17} show that both the metallicity 
and N/O ratio gradients are relatively flat for lower mass galaxies 
($\log(M/M_\odot) = 9$) and steepen with increasing stellar mass.  In SDSS DR7, 
the spectroscopic fiber diameter is 3"; this corresponds to a minimum physical 
diameter of 1.31 $h^{-1}$kpc at a redshift $z < 0.03$.  For most of the dwarf 
galaxies in this study, this contains the majority of their angular size.  
Assuming the abundance gradients remain flat for dwarf galaxies as suggested by 
the results of \cite{Belfiore17}, then our estimates of the gas-phase chemical 
abundances for our sample of dwarf galaxies are independent of the location of 
the spectral fiber on the galaxies' surfaces.

The selection criteria outlined in Section \ref{sec:SDSS_limits} limit our 
sample to only star-forming dwarf galaxies.  As a result, this is not a 
representative sample of the entire dwarf galaxy population.  We are only able 
to discuss the influence of the large-scale environment on star-forming dwarf 
galaxies in this study.  Unfortunately, it is impossible to estimate the 
chemical abundances of red dwarf galaxies with the direct $T_e$ method because 
the UV photons from young stars are needed to excite the interstellar gas.

%-------------------------------------------------------------------------------
\subsection{Dwarf galaxy abundances}

% Results table (machine-readable)
\floattable
\input{results_table_short}

The abundances estimated using the direct $T_e$ method for our dwarf galaxy 
sample are listed in Table \ref{tab:Results}.  Also included are other 
significant characteristics and identification for the galaxies, including their 
large-scale environmental classification.

\subsubsection{Oxygen and nitrogen abundances}

\begin{figure*}
    \centering
    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_12logOHrelations_dust_hist}
    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_12logOHrelations_dust_CDF}
    \caption{Gas-phase metallicity of void dwarf (red solid line) and wall 
    dwarf (black dashed line) galaxies.  A two-sample K-S test of the two data 
    sets results in an asymptotic $p$-value of 0.12, indicating a 12\% 
    probability that a test statistic greater than the observed value of 0.06 
    will be seen if the void sample is drawn from the wall sample.  This is 
    reflected visually, as there appears to be a slight but statistically 
    significant significant large-scale environmental influence on the 
    metallicity of dwarf galaxies.}
    \label{fig:met1sig}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_12logNHrelations_dust_hist}
    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_12logNHrelations_dust_CDF}
    \caption{Abundance of nitrogen relative to hydrogen of void dwarf (red solid 
    line) and wall dwarf (black dashed line) galaxies.  A two-sample K-S test of 
    the two data sets results in an asymptotic $p$-value of 0.015, indicating a 
    1.5\% probability that a test statistic greater than the observed value of 
    0.08 will be seen, if the void sample is drawn from the wall sample.  This 
    is reflected visually, as the void dwarf galaxies appear to have lower 
    values of the N/H ratio than the wall dwarf galaxies.  There is a 
    large-scale environmental dependence of the chemical evolution of dwarf 
    galaxies.}
    \label{fig:N_1sig}
\end{figure*}

The distributions of oxygen and nitrogen abundances for dwarf galaxies as a 
function of large-scale environment are shown in Figures \ref{fig:met1sig} and 
\ref{fig:N_1sig}, respectively.  Both histograms show a slight shift between 
voids and walls in the chemical abundances of dwarf galaxies.  A two-sample 
Kolmogorov-Smirnov (K-S) test quantifies this observation --- a test statistic 
of 0.06 for oxygen and 0.08 for nitrogen are produced, corresponding to a 
probability of 12\% and 1.5\%, respectively, that a test statistic greater than 
or equal that observed will be measured if the void sample were drawn from the 
wall sample.  The cumulative distribution function (CDF) for each of these 
elements can be seen on the right in Figures \ref{fig:met1sig} and 
\ref{fig:N_1sig}; they show that void dwarf galaxies have slightly higher oxygen 
abundances and slightly lower nitrogen abundances than dwarf galaxies in more 
dense regions.  The K-S test quantifies the visual interpretation of these 
figures that the distributions of oxygen and nitrogen abundances are slightly 
different for star-forming dwarf galaxies in voids and walls.

The average and median values of the dwarf galaxy abundances also indicate a 
shift as a result of the large-scale environment.  The average oxygen abundance 
for void dwarf galaxies is $7.99\pm 0.007$ and the median is 8.06, while the 
average oxygen abundance for wall dwarf galaxies is $7.96\pm 0.009$ with a 
median value of 8.04.  This implies that the void dwarf galaxies have higher 
oxygen abundances by about 7\% (average shift of $0.03\pm 0.012$; median shift 
of 0.03) relative to wall dwarf galaxies.  In contrast, the average nitrogen 
abundance for void dwarf galaxies is only $6.55\pm 0.007$ with a median of 6.58, 
while the wall dwarf galaxies have an average nitrogen abundance of 
$6.58\pm 0.008$ and a median of 6.60.  The void dwarf galaxies have lower 
nitrogen abundances by about 10\% (an average shift of $0.04\pm 0.011$ and a 
median shift of 0.02) relative to wall dwarf galaxies.  A tabular version of 
this analysis can be found in Table \ref{tab:stats}.

\subsubsection{Ratio of nitrogen to oxygen}

\begin{figure*}
    \centering
    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_logNOrelations_dust_hist}
    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_logNOrelations_dust_CDF}
    \caption{Ratio of nitrogen to oxygen of void dwarf (red solid line) and wall 
    dwarf (black dashed line) galaxies.  A two-sample K-S test of the two data 
    sets results in an asymptotic $p$-value of $2.6\times 10^{-4}$, indicating 
    only a 0.03\% probability that a test statistic greater than the observed 
    value of 0.10 will be seen.  This is reflected visually, as there is a shift 
    in the N/O ratio between the two populations of dwarf galaxies --- the void 
    galaxies have a lower value of N/O than the wall galaxies.  There is a 
    large-scale influence on the relative chemical abundances of dwarf 
    galaxies.}
    \label{fig:NOratio}
\end{figure*}
